Summary Tables

### 2022-04-22 summary_tables.Rmd
Calculate pa distribution

>>>>

## PA dist
```{r}

### pa distr
cities <- names(io)[!names(io) %in% 'scen_prop']

  # city <- "antofagasta"

  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)

  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)

  l[[city]] <- plyr::rbind.fill(td, td1)

write_csv(data.table::rbindlist(l), "results/multi_city/PA/pa_distr.csv")
```
